Supplmentary Material for DOI:

### 2023-08-01 manuscript/manuscript.qmd
manus

---
title: "Improving Sleep Quality Estimation: A Comparative Study of Machine Learning and Deep Learning Techniques Utilizing Free-Living Accelerometer Data from Thigh-Worn Devices and EEG-Based Sleep Tracking"
author:
  - name: Esben Høegholm Lykke
    email: eskovgaard@health.sdu.dk
    affiliations: 
        - id: some-tech
          name: University of Southern Denmark
          department: Department of Sports Science and Clinical Biomechanics
          address: Campusvej 55
          city: Odense
          state: Denmark
          postal-code: 5230
    attributes:
        corresponding: true
  - name: Jan Christian Brønd
    email: jbrond@health.sdu.dk
    affiliations:
        - id: another-u
          name: University of Southern Denmark
          department: Department of Sports Science and Clinical Biomechanics
          address: Campusvej 55
          city: Odense
          state: Denmark
          postal-code: 5230
abstract: "LÆS IKKE! Dette er volapyk på latin. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Suspendisse vitae dictum eros, ullamcorper elementum orci. Sed laoreet nulla neque, pulvinar fermentum mi iaculis at. Nulla ultricies nibh sit amet vestibulum rutrum. Nam pharetra nisl sed ipsum maximus suscipit. Duis metus nunc, ullamcorper eu mi rutrum, tempus ultricies ante. Nunc vitae lectus nisi. Aliquam efficitur ut eros ut pellentesque. Aenean blandit, nisl nec efficitur interdum, nisi ipsum fermentum dolor, at tempus sem turpis in lacus. Curabitur sollicitudin lectus sit amet velit pellentesque laoreet. Ut posuere diam lobortis nisi eleifend tincidunt. Ut at euismod sem, sed dignissim ligula. Aliquam lacinia massa libero, id eleifend velit pulvinar ac. Fusce volutpat elit eu nulla viverra, nec tempus orci pellentesque."
keywords: 
  - Sleep
  - Accelerometry
  - EEG
  - Machine learning
  - Sleep quality
date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: false
    journal:
      name: npj Digital Medicine
      formatting: preprint
      model: 3p
      cite-style: super
    include-in-header: 
      text: '\usepackage{lineno}\linenumbers'
    fig-pos: 'b'
  docx:
    number-sections: true
editor: 
  markdown: 
    wrap: 72
editor_options: 
  chunk_output_type: inline
---

@@

In this study, data processing of the raw accelerometer data began with
a low-pass filtration step using a 4th order Butterworth filter with a 5
Hz cut-off frequency to eliminate high-frequency noise. Following
filtration, data were partitioned into overlapping 2-second intervals,
each successive interval sharing a 50% overlap with the previous one
similar to methods described by Skotte et al.[@skotte_detection_2014].
Any non-wear data was removed using previously described
methods[@skovgaard2023] and data was resampled to 30-second epochs so
every sample classified by the algorithms corresponds to a 30-second
epoch scored during the ZM recordings. Subsequently, we performed a
feature extraction process that yielded a set of 88 features, providing
a robust characterization of the data. Extracted from accelerometer and
temperature signals, these features include temporal elements that use
both lag and lead values, capturing dynamic data trends by incorporating
measurements from preceding and upcoming epochs. Furthermore, inspired
by Walch et al.[@walch2019], we incorporated sensor-independent features
to encapsulate circadian rhythms. These features offer unique insights
not directly discernible from sensor outputs and are meant to
approximate the changing drive of the circadian clock to sleep over the
course of the night (see @fig-sensor-independent). Furthermore, the
feature set was enriched by including signal characteristics, which
encompass vector magnitude, mean crossing rate, skewness, and kurtosis
for each of the x, y, and z dimensions. All features are summarized in
table ??? **in the supplementary matrials**. Subsequently, we merged the
ZM and corresponding accelerometer recordings. Any overlapping time
between the ZM and accelerometer data was treated as 'in-bed' time, with
the remaining time considered 'out-of-bed'. This process yielded a
dataset providing a around the clock temporal view of each participant's
activity and sleep patterns.

@@

We employed two different model strategies to assess sleep patterns from
thigh-mounted accelerometer data. The first model strategy was designed
as a sequence of two models to simplify the prediction task by
decomposing it into two stages: first predicting 'in-bed' time, then
'sleep' time. In the sequential model the output from the first set of
models, which predicted in-bed time, was subjected to a 5-minute median
filter to eliminate leading and trailing in-bed time blips. This process
enabled us to extract a single continuous time interval that we
identified as the sleep period time window (SPT). The SPT, in turn,
served as the input to the second models in the sequence, enhancing
their predictive accuracy for sleep time. We applied this sequential
strategy using the following four machine learning algorithms:

@@

2.  Decision Tree: Decision trees are capable of handling non-linear
    patterns and are easily interpretable. However, they are prone to
    overfitting, particularly when dealing with complex patterns that
    require simultaneous consideration of multiple features.

@@

For the models in sequence, we trained four pairs of classification
models. Each pair was designed to distinguish between in-bed/out-of-bed
and asleep/awake states, respectively. The dataset was randomly split
into a training set and a testing set, each containing approximately 50%
of the subjects. The splitting of the data was ensured to not have
samples from the same night simultaneously present in both sets. To
optimize hyperparameters, we performed a 10-fold Monte Carlo
cross-validation on a regular grid, i.e., for each hyperparameter, a
range of values at evenly-spaced intervals was selected. comprising 20
different combinations of hyperparameters. The F1 score served as the
optimization metric. The best-performing set of hyperparameters was then
used to fit the models to the full training dataset. This approach
allowed us to maximize performance by leveraging all available data. An
imbalance was observed with the in-bed time determined in the initial
step of the sequential model strategy which after extracting the in-bed
time from the initial sequential models, the imbalance on the resulting
dataset could cause biases during model training, as models may favor
predicting the majority class. To account for this imbalance, we
employed the Synthetic Minority Over-sampling Technique
(SMOTE)[@chawla2002]. SMOTE generates new samples by interpolating
random samples with their nearest neighbors. We utilized the themis R
package[@themis] to implement SMOTE, resulting in a balanced
distribution of training samples across both classes.

@@

To assess the performance of our models in deriving sleep quality
metrics, we utilized Bland-Altman plots and Pearson correlations. The
Bland-Altman method was employed specifically to determine the level of
agreement between two measurement techniques. Given the nature of our
dataset, which contains multiple observations per subject, we employed a
bootstrap procedure to account for this added variability. We first
calculated the mean difference (bias) and then defined the limits of
agreement (LOA) as the mean difference plus or minus 1.96 times the
standard deviation of these differences. Acknowledging the possibility
of non-normality and potential skewness in our data, we chose to apply a
bias-corrected and accelerated (BCa) bootstrap
method[@diciccio_bootstrap_1996]. This approach allowed us to better
address potential bias in our estimates and the inherent intra-subject
variability. Utilizing 10,000 bootstrap replicates, we estimated the 95%
confidence intervals for both the bias and the LOA, thus ensuring
robustness in our measurements. The sleep quality parameteres included
are defined as follows in accordance with the ZM definitions:

@@

```{r}
#| echo: false
#| message: false
#| label: tbl-in_bed_performance
#| tbl-cap: In-bed performance metrics

@@

```{r}
#| echo: false
#| message: false
#| tbl-colwidths: auto
#| label: tbl-sleep_performance
#| tbl-cap: Performance of the sleep/wake classification of the sequential models.

@@

A complete set of confusion matrices generated from data both containing
the out-of-bed and in-bed time are presented in @fig-conf_mat. The
figure shows favorable epoch-to-epoch performance across all sequential
models, however, it is evident that the biLSTM is less successful in
classifying the in-bed-awake class which cannot be deduced from the
confusion matrices from the sequential models.

![Confusion matrices for binary sleep prediction. The middle of each
tile is the normalized count (overall percentage) and, beneath it, the
count. The bottom number is the column percentage (target). At the right
side of each tile is the row percentage (prediction). i) decision tree,
ii) logistic regression, iii) feed-forward neural net, iv) XGBoost, and
v) biLSTM.](visuals/all_conf_mats.pdf){#fig-conf_mat}

@@

@tbl-ba_cor presents a comparative analysis of the included models used
to predict various sleep quality metrics (SPT, TST, SE, LPS, WASO) using
the 5-minute median filtered ZM predictions. To see the full table
including models developed from raw ZM predictions and 10-minute median
filtered ZM predictions, see **\[SUPP. MAT.\]**. In terms of bias, the
decision tree model consistently underestimated SPT, TST, and SE, and
overestimated LPS and WASO in comparison to ZM. The logistic regression
model had similar trends, with more pronounced underestimation in TST
and overestimation in LPS. The feed-forward neural network also
exhibited similar bias as the decision tree and the logistic regression
models, but with a higher overestimation in WASO. On the other hand, the
XGBoost model showed least bias among all, especially in its 5-minute
median predictions. Considering LOA, the decision tree had higher
variability across different sleep quality metrics and filtering
techniques, particularly for LPS and WASO, which indicates lower
agreement with ZM. Other models had comparable LOA but with notable
exceptions. For example, TST LOA for the logistic regression model was
particularly wide in the 5-minute median predictions. Correlation-wise,
the pearson coefficient, revealed that the XGBoost model consistently
had the highest correlation with ZM across all sleep quality metrics and
filtering methods Notably, the XGBoost's 5-minute median predictions
showed the strongest correlation (0.66) for TST among all models and
filtering techniques.

```{r}
#| echo: false
#| message: false
#| label: tbl-ba_cor
#| tbl-cap: Summary of Bias, Limits of Agreement, and Pearson Correlation for various Sleep Parameter Predictions (SPT, TST, SE, LPS, WASO) using different Machine Learning Models (Decision Tree, Logistic Regression, Feed-Forward Neural Net, XGBoost) with Raw ZM Predictions, 5-Min and 10-Min Median as predictors. Each value is provided with its 95% Confidence Interval (CI).

@@

@fig-xgb_ba_cor shows the agreement between the XGBoost model, trained
on 5-minute median filtered ZM predictions, and the 5-minute
median-smoothed ZM-derived sleep quality metrics. The Bland-Altman plot
for the SPT and TST reveals a good level of agreement with the ZM, as
evidenced by a bias close to zero. Interestingly, a portion of the data
points are located near the zero line indicating perfect agreement. The
scatterplot for SPT also demonstrates a positive trend, indicating a
moderate linear correlation between the XGBoost model and the ZM-derived
sleep quality metrics. The bias and LOA for TST are comparable to those
observed for SPT, indicating a consistent level of agreement between the
two methods. The scatterplot for TST also shows a slightly higher
correlation, primarily driven by the absence of extreme
outliers.Furthermore, the remaining three sleep quality metrics, SE,
LPS, and WASO, exhibit heteroscedasticity in contrast to SPT and TST.
This outcome is expected as achieving 100% sleep efficiency is
relatively rare, resulting in less disagreement between the methods as
values approach the upper limit. Conversely, as sleep efficiency
decreases, the potential for discrepancies and differing interpretations
between the methods increases, leading to greater heteroscedasticity. A
moderate positive linear correlation is observed between the XGBoost
model and ZM-derived sleep quality metrics for SE, however, a poor
correlation is observed for LPS and WASO. Similar plots for all models
are available in the **supplementary materials (75 plots. Jeg ved ikke
om nogen orker at bladre igennem dem).**

@@

In conclusion, our study contributes to the ongoing efforts to improve
sleep estimation methods using thigh-worn accelerometers. We evaluated
different machine learning models for predicting in-bed and sleep times
and their corresponding sleep quality metrics. While the sequential
models generally demonstrated excellent performance in predicting in-bed
time, they faced challenges in accurately distinguishing between sleep
and wake epochs during in-bed time. Among all models and configurations
evaluated, the XGBoost model exhibited superior performance across all
performance metrics, including epoch-to-epoch predictions and sleep
quality parameter derivatives. Our research also highlighted the current
limitations of sleep detection methods, such as challenges in
effectively detecting wake periods during in-bed time and the need for
further improvements to increase the precision of individual sleep
assessments. We believe our work lays the groundwork for future research
to further refine and improve the performance of these models,
contributing to a more precise and accurate evaluation of sleep patterns
and quality using thigh-worn accelerometers.

>>>>

---
title: "Improving Sleep Quality Estimation: A Comparative Study of Machine Learning and Deep Learning Techniques Utilizing Free-Living Accelerometer Data from Thigh-Worn Devices and EEG-Based Sleep Tracking"
author:
  - name: Esben Høegholm Lykke
    email: eskovgaard@health.sdu.dk
    affiliations: 
        - id: some-tech
          name: University of Southern Denmark
          department: Department of Sports Science and Clinical Biomechanics
          address: Campusvej 55
          city: Odense
          state: Denmark
          postal-code: 5230
    attributes:
        corresponding: true
  - name: Jan Christian Brønd
    email: jbrond@health.sdu.dk
    affiliations:
        - id: another-u
          name: University of Southern Denmark
          department: Department of Sports Science and Clinical Biomechanics
          address: Campusvej 55
          city: Odense
          state: Denmark
          postal-code: 5230
abstract: "Studying sleep is vital in health research, but the gold standard, polysomnography, is costly and impractical for large-scale studies. An affordable alternative is using wearable accelerometers. While wrist and hip-worn devices are commonly used in sleep research, thigh-worn accelerometers have been relatively unexplored. Our study evaluated machine learning and deep learning models utilizing data from thigh-worn accelerometers to estimate sleep and sleep quality metrics, comparing them with an EEG-based sleep monitor. The dataset consisted of data from 585 days and nights, comprising accelerometry and EEG-based sleep estimates from children aged 6-10. We employed both sequential and multiclass model strategies on both raw and filtered data. The most effective model was XGBoost, which performed well when applied to 5-minute median filtered data, exhibiting small biases in sleep period time (0.2 minutes), total sleep time (-7 minutes), sleep efficiency (-1.1%), and wake after sleep onset (-0.9 minutes). Furthermore, the XGBoost model showed a robust correlation (0.66, 95% CI: 0.61 - 0.7) with total sleep time, indicating its potential. However, despite these favorable results in bias, our study revealed large limits of agreements in accordance with previous research on hip- and wrist-worn devices. In conclusion, we present promising results in using machine learning technieques to estimate sleep quality metrics, however, accurately classifying awake periods during in-bed time remained challenging. Moreover, additional improvements are necessary to precisely assess individual sleep quality metrics due to the notable limits of agreement."
keywords: 
  - Sleep
  - Accelerometry
  - EEG
  - Machine learning
  - Sleep quality
date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: false
    journal:
      name: npj Digital Medicine
      formatting: preprint
      model: 3p
      cite-style: super
    include-in-header: 
      text: '\usepackage{lineno}\linenumbers'
    fig-pos: 'b'
  docx:
    number-sections: true
editor: 
  markdown: 
    wrap: 72
editor_options: 
  chunk_output_type: inline
---

@@

In this study, data processing of the raw accelerometer data began with
a low-pass filtration step using a 4th order Butterworth filter with a 5
Hz cut-off frequency to eliminate high-frequency noise. Following
filtration, data were partitioned into overlapping 2-second intervals,
each successive interval sharing a 50% overlap with the previous one
similar to methods described by Skotte et al.[@skotte_detection_2014].
Any non-wear data was removed using previously described
methods[@skovgaard2023] and data was resampled to 30-second epochs so
every sample classified by the algorithms corresponds to a 30-second
epoch scored during the ZM recordings. Subsequently, we performed a
feature extraction process that yielded a set of 88 features, providing
a robust characterization of the data. Extracted from accelerometer and
temperature signals, these features include temporal elements that use
both lag and lead values, capturing dynamic data trends by incorporating
measurements from preceding and upcoming epochs. Furthermore, inspired
by Walch et al.[@walch2019], we incorporated sensor-independent features
to encapsulate circadian rhythms. These features offer unique insights
not directly discernible from sensor outputs and are meant to
approximate the changing drive of the circadian clock to sleep over the
course of the night (see @fig-sensor-independent). Furthermore, the
feature set was enriched by including signal characteristics, which
encompass vector magnitude, mean crossing rate, skewness, and kurtosis
for each of the x, y, and z dimensions. Subsequently, we merged the ZM
and corresponding accelerometer recordings. Any overlapping time between
the ZM and accelerometer data was treated as 'in-bed' time, with the
remaining time considered 'out-of-bed'. This process yielded a dataset
providing a around the clock temporal view of each participant's
activity and sleep patterns.

@@

We employed two different model strategies to assess sleep patterns from
thigh-mounted accelerometer data. The first model strategy was designed
as a sequence of two models, each functioning as a binary classifier.
This approach aimed to simplify the prediction task by decomposing the
multiclass problem of classifying 'out-of-bed-awake', 'in-bed-awake',
and 'in-bed-asleep' into two binary stages: first predicting 'in-bed'
time, then 'sleep' time. The output from the first set of binary
classifiers, which predicted in-bed time, was subjected to a 5-minute
median filter to remove transient in-bed time blips. This process
enabled us to establish a single continuous time interval that we
identified as the sleep period time window (SPT). The SPT then served as
the input for the second stage of binary classifiers in the sequence,
further enhancing their predictive accuracy for sleep time." We applied
this sequential strategy using the following four machine learning
algorithms:

@@

2.  Decision Tree: Decision trees are capable of handling non-linear
    patterns and are easily interpretable. However, they are prone to
    overfitting, particularly when dealing with complex patterns that
    require simultaneous consideration of multiple features. In the
    current study, we used a maximum tree depth of 8.

@@

We trained four pairs of models in sequence, with each pair
distinguishing between in-bed/out-of-bed and asleep/awake states,
respectively. We divided our dataset randomly into a training set and a
testing set, with each containing roughly half of the subjects. The
splitting of the data was ensured to not have samples from the same
night simultaneously present in both sets. To optimize hyperparameters,
we performed a 10-fold Monte Carlo cross-validation on a regular grid
(i.e., for each hyperparameter, a range of values at evenly-spaced
intervals was selected) comprising 20 different combinations of
hyperparameters. The F1 score served as the optimization metric. The
best-performing set of hyperparameters was then used to fit the models
to the full training dataset. This approach allowed us to maximize
performance by leveraging all available training data to estimate the
model parameters. An imbalance was observed with the in-bed time
determined in the initial step of the sequential model strategy which
after extracting the in-bed time from the initial sequential models, the
imbalance on the resulting dataset could cause biases during model
training, as models may favor predicting the majority class. To account
for this imbalance, we employed the Synthetic Minority Over-sampling
Technique (SMOTE)[@chawla2002]. SMOTE generates new samples by
interpolating random samples with their nearest neighbors. We utilized
the themis R package[@themis] to implement SMOTE, resulting in a
balanced distribution of training samples across both classes.

@@

To assess the performance of our models in deriving sleep quality
metrics, we utilized Bland-Altman plots and Pearson correlations. The
Bland-Altman method was employed specifically to determine the level of
agreement between two measurement techniques. Given the nature of our
dataset, which contains multiple observations per subject but
necessarily equal number, we employed a bootstrap procedure to account
for this added variability. We first calculated the mean difference
(bias) and then defined the limits of agreement (LOA) as the mean
difference plus or minus 1.96 times the standard deviation of these
differences. Acknowledging the possibility of non-normality and
potential skewness in our data, we chose to apply a bias-corrected and
accelerated (BCa) bootstrap method[@diciccio_bootstrap_1996]. This
approach allowed us to better address potential bias in our estimates
and the inherent intra-subject variability. Utilizing 10,000 bootstrap
replicates, we estimated the 95% confidence intervals for both the bias
and the LOA, thus ensuring robustness in our measurements. The sleep
quality metrics included are defined as follows in accordance with the
ZM definitions:

@@

```{r}
#| echo: false
#| message: false
#| label: tbl-in_bed_performance
#| tbl-cap: Performance metrics of the classification of in-bed/out-of-bed time of the included models.

@@

```{r}
#| echo: false
#| message: false
#| tbl-colwidths: auto
#| label: tbl-sleep_performance
#| tbl-cap: Performance metrics of the sleep/wake classification of the included models.

@@

A complete set of confusion matrices generated from data both containing
the out-of-bed and in-bed time are presented in @fig-conf_mat. These
matrices showcase the epoch-to-epoch performance of all sequential
models in distinguishing between 'awake' and 'asleep' states, regardless
of whether the subject is 'in-bed' or 'out-of-bed'. However, it's
important to note that the binary nature of these sequential models
means they cannot provide direct information about the classification of
the 'in-bed-awake' state. In contrast, the biLSTM model, which also
categorizes the 'in-bed-awake' state as a distinct class, appears to
have less success in classifying this particular state.

![Confusion matrices for binary sleep prediction. The middle of each
tile is the normalized count (overall percentage). The bottom number of
each tile is the column percentage and the right side of each tile is
the row percentage. i) decision tree, ii) logistic regression, iii)
feed-forward neural net, iv) XGBoost, and v)
biLSTM.](visuals/all_conf_mats.pdf){#fig-conf_mat}

@@

@tbl-ba_cor presents a comparative analysis of the included models used
to predict various sleep quality metrics (SPT, TST, SE, LPS, WASO) using
the 5-minute median filtered ZM predictions. To see the full table
including models developed from raw ZM predictions and 10-minute median
filtered ZM predictions, see table 1 in supplementary materials. In
terms of bias, the decision tree model consistently underestimated SPT,
TST, and SE, and overestimated LPS and WASO in comparison to ZM. The
logistic regression model had similar trends, with more pronounced
underestimation in TST and overestimation in LPS. The feed-forward
neural network also exhibited similar bias as the decision tree and the
logistic regression models, but with a higher overestimation in WASO. On
the other hand, the XGBoost model showed least bias among all,
especially in its 5-minute median predictions. Considering LOA, the
decision tree had higher variability across different sleep quality
metrics and filtering techniques, particularly for LPS and WASO, which
indicates lower agreement with ZM. Other models had comparable LOA but
with notable exceptions. For example, TST LOA for the logistic
regression model was particularly wide in the 5-minute median
predictions. Correlation-wise, the pearson coefficient, revealed that
the XGBoost model consistently had the highest correlation with ZM
across all sleep quality metrics and filtering methods Notably, the
XGBoost's 5-minute median predictions showed the strongest correlation
(0.66) for TST among all models and filtering techniques.

```{r}
#| echo: false
#| message: false
#| label: tbl-ba_cor
#| tbl-cap: Summary of bias, limits of agreement, and pearson correlation for various sleep parameter predictions (SPT, TST,SE, LPS, WASO) using different machine learning and deep learning models (decision tree, logistic regression, feed-forward neural network, XGBoost) on raw ZM predictions, 5-minute and 10-minute median predictions. Each value is provided with its 95% confidence interval (CI).

@@

@fig-xgb_ba_cor shows the agreement between the XGBoost model, trained
on 5-minute median filtered ZM predictions, and the 5-minute
median-smoothed ZM-derived sleep quality metrics. The Bland-Altman plot
for the SPT and TST reveals a good level of agreement with the ZM, as
evidenced by a bias close to zero. Interestingly, a portion of the data
points are located near the zero line indicating perfect agreement. The
scatterplot for SPT also demonstrates a positive trend, indicating a
moderate linear correlation between the XGBoost model and the ZM-derived
sleep quality metrics. The bias and LOA for TST are comparable to those
observed for SPT, indicating a consistent level of agreement between the
two methods. The scatterplot for TST also shows a slightly higher
correlation, primarily driven by the absence of extreme
outliers.Furthermore, the remaining three sleep quality metrics, SE,
LPS, and WASO, exhibit heteroscedasticity in contrast to SPT and TST.
~~This outcome is expected as achieving 100% sleep efficiency is
relatively rare, resulting in less disagreement between the methods as
values approach the upper limit. Conversely, as sleep efficiency
decreases, the potential for discrepancies and differing interpretations
between the methods increases, leading to greater heteroscedasticity.~~
A moderate positive linear correlation is observed between the XGBoost
model and ZM-derived sleep quality metrics for SE, however, a poor
correlation is observed for LPS and WASO.

@@

In conclusion, our study contributes to the ongoing efforts to improve
sleep estimation methods using thigh-worn accelerometers. We evaluated
different machine learning and deep learnng models for predicting in-bed
and sleep times and their corresponding sleep quality metrics. While the
sequential models generally demonstrated excellent performance in
predicting in-bed time, they faced challenges in accurately
distinguishing between sleep and wake epochs during in-bed time. Among
all models and configurations evaluated, the XGBoost model exhibited the
best performance, including epoch-to-epoch predictions and sleep quality
metrics. Our research also highlighted the current limitations of sleep
detection methods, such as challenges in effectively detecting wake
periods during in-bed time and the need for further improvements to
increase the precision of individual sleep assessments. We believe our
work lays the groundwork for future research to further refine and
improve the performance of these models, contributing to a more precise
and accurate evaluation of sleep patterns and quality using thigh-worn
accelerometers.

### 2023-08-01 manuscript/supp_mat/supp.qmd
manus

@@

![all ba and scatterplots](../visuals/all_ba_scatterplots.pdf)

>>>>

Table of features? Er det nødvendigt?

@@

Plots similar to figure 5 for all model and filtering combinations (75 plots in total) are available upon request.

<!-- ![Decision tree, raw](../visuals/raw_decision_tree_ba_cor.pdf){#tbl-raw_dc} -->
<!-- ![Decision tree, median_5](../visuals/median_5_decision_tree_ba_cor.pdf){#tbl-m5_dc} -->
<!-- ![Decision tree, median_10](../visuals/median_10_decision_tree_ba_cor.pdf){#tbl-m10_dc} -->

<!-- ![Logistic regression, raw](../visuals/raw_logistic_regression_ba_cor.pdf) -->
<!-- ![Logistic regression, median_5](../visuals/median_5_logistic_regression_ba_cor.pdf) -->
<!-- ![Logistic regression, median_10](../visuals/median_10_logistic_regression_ba_cor.pdf) -->

<!-- ![Neural_network, raw](../visuals/raw_neural_network_ba_cor.pdf) -->
<!-- ![Neural_network, median_5](../visuals/median_5_neural_network_ba_cor.pdf) -->
<!-- ![Neural_network, median_10](../visuals/median_10_neural_network_ba_cor.pdf) -->

<!-- ![XGBoost, raw](../visuals/raw_xgboost_ba_cor.pdf) -->
<!-- ![XGBoost, median_5](../visuals/median_5_xgboost_ba_cor.pdf) -->
<!-- ![XGBoost, median_10](../visuals/median_10_xgboost_ba_cor.pdf) -->

<!-- ![biLSTM, raw](../visuals/raw_biLSTM_ba_cor.pdf) -->
<!-- ![biLSTM, median_5](../visuals/median_5_biLSTM_ba_cor.pdf) -->
<!-- ![biLSTM, median_10](../visuals/median_10_biLSTM_ba_cor.pdf) -->
